Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2014-12-21 wearables_survey.tex
Added the appendixes

\subsection{Validation}
(REDO) We conducted a focus group to look over the list, brainstorm more scenarios,  and get question feedback. We got a small sample of results (which were guided so we through them out, but it was helpful to know what we might expect) and clarify any scenarios which were unclear. Logistically, we also used this time to time the survey, made sure the survey worked, and other things. Quick demographics of the focus group here--(fix later) 12 people, X\% male, average age Y, with education ranging from A to B and professions including student, artist, business person, court judge, etc.  You can look at the focus group script in appendix \ref{sec:script}.

@@

%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Focus Group Script}
\label{sec:script}

text text

\section{Fischoff Prompts}
\label{sec:prompt}

text text

@@

text text

@@

text text
%\section{Detailed Tech Rankings}

@@

% That's all folks!
\end{document}

>>>>

\subsection{Validation}
(REDO) We conducted a focus group to look over the list, brainstorm more scenarios,  and get question feedback. We got a small sample of results (which were guided so we through them out, but it was helpful to know what we might expect) and clarify any scenarios which were unclear. Logistically, we also used this time to time the survey, made sure the survey worked, and other things. Quick demographics of the focus group here--(fix later) 12 people, X\% male, average age Y, with education ranging from A to B and professions including student, artist, business person, court judge, etc.  .

@@

%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Fischoff Prompts}
\label{sec:prompt}

BENEFIT:

``We would like to ask you to rate the benefits associated with each of the following technologies.

Consider all types of benefits: how many jobs are created, how much money is generated directly or indirectly, how much enjoyment is brought to people, how much a contribution is made to the people's health and welfare, what this technology promotes, and so on. (e.g. for swimming, consider the manufacture and sale of swimsuits, the time spent exercising, the social interactions during swimming, and the sport created around the activity.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible benefits.

Do not consider the costs or risks associated with these items. It is true, for example, that sometimes swimmers can drown. But evaluating such risks is not your present job. Your job is to assess the gross benefits, not the net benefits which remain after the costs and risks are subtracted out.

Please rate the following technologies below with a number. We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you. Start with the least beneficial technology at 10 and assign higher numbers for the more beneficial technologies. (For instance, a technology rated 34 is twice as beneficial as a technology rated 17)''

RISK:

``We would like to ask you to rate the risks associated with each of the following technologies.

Consider all types of risks: the risk of physical harm or death, the risk to others or bystanders, the financial cost of the technology, any distress caused by the technology, what the consequences would be if the technology was misused, any impact on the public, work, or personal life, and other considerations. (e.g. for electricity, consider the risk of electrocution, the pollution caused by coal, the risk that miners need to take to mine the coal, the cost to build the infrastructure to deliver electricity, etc.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible risks.

Do not consider the costs or benefits associated with these items. It is true, for example, that electricity also creates a market for home appliances. But evaluating such benefits is not your present job. Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.

Please rate the following technologies below with a number. We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you. Start with the least risky technology at 10 and assign higher numbers for the more risky technologies. (For instance, a technology rated 14 is half as risky as a technology rated 28.)''

@@

BENEFIT:

technology 	median	25\%		75\% \\
electricity	87	50	100\\
internet	65	45	100\\
laptops	60	40	80\\
email	50	30	75\\
smartphones	50	32.5	75\\
location tracking	40	20	67.5\\
heart rate detection	40	28	62.5\\
language detection	35	15	60\\
voice recognition	25	15	40\\
speech to text	25	15	36.25\\
lawnmowers	24	15	40\\
facial recognition	22	13	40\\
guns	20	10	30\\
motrocycles	20	12	40\\
voice based emotion detection	20	10	30\\
facial detection	20	10	32\\
discrete camera	20	15	30\\
smartwatches	20	10	32.5\\
google glass	20	12	40\\
fitness trackers	19	10	30\\
cubetastic	18	10	30\\
discrete microphone	15	10	20\\
age detection	12	10	21\\
gender detection	10	10	15

RISK:

technology 	median	25\%		75\%\\
guns	60	40	80\\
motrocycles	45	27	70\\
electricity	25	15	40\\
lawnmowers	20	12	30\\
facial recognition	17	12.5	30\\
internet	15	10	30\\
discrete camera	12	10	30\\
location tracking	10	10	20\\
age detection	10	10	15\\
gender detection	10	10	12\\
language detection	10	10	10\\
voice based emotion detection	10	10	15\\
facial detection	10	10	25\\
voice recognition	10	10	15\\
heart rate detection	10	10	10\\
email	10	10	16\\
speech to text	10	10	10\\
discrete microphone	10	10	20\\
smartphones	10	10	19\\
laptops	10	10	15\\
fitness trackers	10	10	10\\
smartwatches	10	10	10\\
google glass	10	10	20\\
cubetastic	10	10	30

@@

Privacy: ``privacy,'' revealing personal information, spying. \\
Security:  ``security,'' compromise, malware, hacking. \\
GPS tracking: ``location,'' ``GPS,'' being monitored.

Unaware use: using data without permission or in a different way than understood by user. \\
Unaware collection: collecting data without permission. \\
Unaware access: disclosure of data without permission. \\
False information: inaccurate or maliciously false data.

Health Risk: radiation, cancer, or long-term effects.\\
Safety: distractions causing car crashes or injuries, mugging or violence because of the device, injuries from device malfunctions (battery burns).\\
Discomfort: eye strain, headache, obscured vision, irritation. \\
Financial cost: getting ripped off by buying the device or device accessories, having to buy another device when broken or stolen, financial compromise caused by device. \\
Theft: the device getting stolen.

Social Impact: dependency, distance from friends and family, changes in decision making, social changes, etc. \\
Social Stigma: judgment, hate, or bystander discomfort.\\ 
Aesthetics: fashion, the device being ugly, mentions of not looking cool/dorky.

Miscellaneous: odd comments, uncommon concerns. \\
None: ``None,'' no threat, perceiving no big concerns \\
Don't know: ``do not know,'' hinting at confusion \\
Don't care: `` do not care,'' nonchalant answers

%\section{Detailed Tech Rankings}

@@

% That's all folks!
\end{document}
\\
